Preprocessing summary

### 2018-10-10 inst/examples/summary.Rmd
ok

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

>>>>

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, publication_country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
